PWD.KAZ

### 2019-07-19 results/PWD.KAZ.BivData.Rmd
cleaning up files and made some additions to analyses files

#load MLH1 data
#setwd("C:/Users/April/Desktop/MLH1repo/") #don't have two
load(file="~./MLH1repo/data/MLH1/MLH1_data_setup_62419.RData")
#MLH1_data_setup_62419.RData
#KAZ_male_data = read.csv("~./data/KAZ_BivData.csv")
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)

@@

#make indevidal DFs by strain just in case...
PWD.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "PWD",]
KAZ.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "KAZ",]

@@

#Isolate cells with all (19) autosomes measured
whole.cell_table <- Auto.Man_BivData_cells[Auto.Man_BivData_cells$number > 17,]
whole.cell_table <- whole.cell_table[whole.cell_table$number < 21,]
whole.cell.list <- unique(whole.cell.DF$fileName)

@@

#make the bins
short.bin.Bivs <- whole.cell.DF[whole.cell.DF$rank < 6,]
long.bin.Bivs <- whole.cell.DF[whole.cell.DF$rank > 14,]

@@

#make whole cell melt
whole.cell_melt.DF <- Auto.Man_BivData.melt[Auto.Man_BivData.melt$fileName %in% whole.cell.list,]
#add rank to these measures
whole.cell_melt.DF <- ddply(whole.cell_melt.DF, .(fileName), transform, rank = rank(chromosomeLength,ties.method ="min")-1)

@@

save.image("data/MLH1/MLH1_data_setup_62419.RData")
```

```{r SClength.cell.tables}
#this is useful for making the list of cells to curate (comment out after curation step)

@@

PWD and KAZ differ in gwRR/MLH1 counts, is there a correlation in meiotic features which go with expected differences in gwRR.

>>>>

#load MLH1 data
#setwd("C:/Users/April/Desktop/MLH1repo/") #don't have two

#DONT LOAD MLH1 yet -- keep these seperate for now
#load(file="~./MLH1repo/data/MLH1/MLH1_data_setup_62419.RData")
#MLH1_data_setup_62419.RData
#KAZ_male_data = read.csv("~./data/KAZ_BivData.csv")
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)

@@

#make indevidal DFs by strain just in case...
PWD.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "PWD",]
KAZ.BivData.Hand_measures <- HandMeasures_BivData[HandMeasures_BivData$strain == "KAZ",]
```

ToDo:
  -add in IFD calqs
  -add rbar calqs
  -make the basic plots ect

@@

#Isolate cells with all (19) autosomes measured
whole.cell_table <- Auto.Man_BivData_cells[Auto.Man_BivData_cells$number > 17,]
whole.cell_table <- whole.cell_table[whole.cell_table$number < 21,]
whole.cell.list <- unique(whole.cell_table$fileName)

@@

#make the bins
short.bin.Bivs <- whole.cell.DF[whole.cell.DF$rank < 6,]
long.bin.Bivs <- whole.cell.DF[whole.cell.DF$rank > 14,]
```

@@

#make whole cell melt
whole.cell_melt.DF <- Auto.Man_BivData.melt[Auto.Man_BivData.melt$fileName %in% whole.cell.list,]
#add rank to these measures
whole.cell_melt.DF <- ddply(whole.cell_melt.DF, .(fileName), transform, rank = rank(chromosomeLength,ties.method ="min")-1)
```

@@

save.image("~./MLH1repo/data/BivData/PWD.KAZ_BivData_data.RData")
```

    -for all measures with passing foci, add IFD and rbar!

    4B. whole.cell melted table

### Analysis and Such

PWD and KAZ differ in gwRR/MLH1 counts, is there a correlation in meiotic features which go with expected differences in gwRR.
```{r SClength.cell.tables}
#this is useful for making the list of cells to curate (comment out after curation step)

@@
